---
title: "Hw4-2"
author: "Yiji Gao"
date: "5/1/2022"
output: md_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


# Question 2
## Part 1 Import the data

```{r message=FALSE, warning=FALSE, echo=FALSE}
library(mvtnorm)
library(ggplot2)
library(LICORS)
library(foreach)
library(mosaic)

social_market = read.csv('https://raw.githubusercontent.com/jgscott/ECO395M/master/data/social_marketing.csv')

```



## Part 2 Wrangle the data

In the part, chatter and uncategorized column are deleted because they are meaningless to this research. At the same time, spam is limited to be equal to 0 and adult is limited to be smaller than 10 so that some kind of "bots" are excluded. As a result, the data is most useful.

```{r message=FALSE, warning=FALSE, echo=FALSE}

social_market1 = subset(social_market, select = -c(chatter,uncategorized) )
social_market1 = social_market1[-c(1)]

data=social_market1 %>%
  filter(spam==0& adult<10)
```

## Part 3 Cluster

In this part, all people are divided into 5 groups using K-means method. Photo_sharing, politics, business and crafts are chosen to make the graph, having a rough understanding of the respondents.

```{r message=FALSE, warning=FALSE, inculde=FALSE}

SM = scale(social_market1, center=TRUE, scale=TRUE)

mu = attr(SM,"scaled:center")
sigma = attr(SM,"scaled:scale")

clust1 = kmeans(SM, 5, nstart=25)

qplot(photo_sharing, politics, data=social_market1, color=factor(clust1$cluster))
qplot(business, crafts, data=social_market1, color=factor(clust1$cluster))

ggplot(social_market1) + 
  geom_point(aes(photo_sharing, politics, color=factor(clust1$cluster)))

```


## Part 4 Groups

```{r message=FALSE, warning=FALSE, include=FALSE}

which(clust1$cluster == 1)
which(clust1$cluster == 2)
which(clust1$cluster == 3)
which(clust1$cluster == 4)
which(clust1$cluster == 5)

```

All data, followers of Twitter account of a large consumer drinks brand, are divided into 5 categories. The number in the category from most to least is category 4, 2, 3, 1, 5, and the number of category 4 is much more than others. Separately, in group 1, people are more interested in travel, politics and news. In group2, people show more passion on health nutrition, personal fitness. In group3, individual are more concerned about sports fandom, food, family, health nutrition and religion. For members of group 4, photo sharing is the most frequent object they mention while the whole number of twitter is not very high. In group 5, photo sharing, shopping, cooking, beauty and fashion have high frequency. 


## Part 5 Report


To appeal to group1, the brand can combine the product with the trending
To appeal to group2, the brand can focus on the nutrition of the product and describe how healthy the product is. 
To appeal to group3, the brand can make the advertisement showing that family members share the product together. As a result, the product can leave people the impression of being together.
To appeal to group4, the brand can pay more attention to the package of the product so that it books beautiful and can be shared. 
To appeal to group5, modern and fashion play important roles so that the promotion should be young.

